% !TEX root = ../main.tex

\hitszsetup{
  %******************************
  % 注意：
  %   1. 配置里面不要出现空行
  %   2. 不需要的配置信息可以删除
  %******************************
  %
  %=====
  % 秘级
  %=====
  statesecrets={公开},
  natclassifiedindex={TM301.2},
  intclassifiedindex={62-5},
  %
  %=========
  % 中文信息
  %=========
  ctitleone={基于神经网络的},%本科生封面使用
  ctitletwo={机器人智能抓取研究},%本科生封面使用
  ctitlecover={基于神经网络的机器人智能抓取研究},%放在封面中使用，自由断行
  ctitle={基于神经网络的机器人智能抓取研究},%放在原创性声明中使用
  csubtitle={一条副标题}, %一般情况没有，可以注释掉
  cxueke={工学},
  csubject={机械设计制造及其自动化},
  caffil={机电工程与自动化学院},
  cauthor={杨敬轩},
  csupervisor={某某某 教授},
  cassosupervisor={某某某 教授}, % 副指导老师
  ccosupervisor={某某某 教授}, % 联合指导老师
  % 日期自动使用当前时间，若需指定按如下方式修改：
  %cdate={超新星纪元},
  cstudentid={SZ160310217},
  cstudenttype={同等学力人员}, %非全日制教育申请学位者
  %（同等学力人员）、（工程硕士）、（工商管理硕士）、
  %（高级管理人员工商管理硕士）、（公共管理硕士）、（中职教师）、（高校教师）等
  %
  %
  %=========
  % 英文信息
  %=========
  etitle={Research on robot intelligent grasping based on Neural Network},
  esubtitle={This is the sub title},
  exueke={Engineering},
  esubject={Mechanical Design, Manufacturing and Automation},
  eaffil={\emultiline[t]{School of Mechanical Engineering\\ and Automation}},
  eauthor={Jingxuan Yang},
  esupervisor={Professor XXX},
  eassosupervisor={XXX},
  % 日期自动生成，若需指定按如下方式修改：
  edate={June, 2020},
  estudenttype={Master of Art},
  %
  % 关键词用“英文逗号”分割
  ckeywords={\TeX, \LaTeX, CJK, 论文模板, 毕业论文},
  ekeywords={\TeX, \LaTeX, CJK, hitszthesis, thesis},
}

% 中文摘要
\begin{cabstract}

  摘要的字数（以汉字计），硕士学位论文一般为500 $\sim$ 1000字，博士学位论文为1000 $\sim$ 2000字，均以能将规定内容阐述清楚为原则，文字要精练，段落衔接要流畅。摘要页不需写出论文题目。英文摘要与中文摘要的内容应完全一致，在语法、用词上应准确无误，语言简练通顺。留学生的英文版博士学位论文中应有不少于3000字的“详细中文摘要”。

  关键词是为了文献标引工作、用以表示全文主要内容信息的单词或术语。关键词不超过5个，每个关键词中间用分号分隔。（模板作者注：关键词分隔符不用考虑，模板会自动处理。英文关键词同理。）

\end{cabstract}

% 英文摘要
\begin{eabstract}

  An abstract of a dissertation is a summary and extraction of research workand contributions. Included in an abstract should be description of researchtopic and research objective, brief introduction to methodology and research process, and summarization of conclusion and contributions of the research. An abstract should be characterized by independence and clarity and carry identical information with the dissertation. It should be such that the general idea and major contributions of the dissertation are conveyed without reading the dissertation.

  An abstract should be concise and to the point. It is a misunderstanding to make an abstract an outline of the dissertation and words ``the first chapter'', ``the second chapter'' and the like should be avoided in the abstract.

  Key words are terms used in a dissertation for indexing, reflecting core information of the dissertation. An abstract may contain a maximum of 5 key words, with semi-colons used in between to separate one another.

\end{eabstract}
